Review Manuscript

### 2019-04-04 review_article.Rmd
Bibliography information

---
title: "Review Manuscript"
author: "Stephanie"
date: "02/04/2019"
output: html_document
---

>>>>

---
title: "Review Manuscript"
author: "Stephanie"
date: "02/04/2019"
output: html_document

toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
bibliography: reviewbib.bib
biblio-style: vancouver
link-citations: true
---
